Studying the Performance of the Jellyfish Search Optimiser for the Application of Projection Pursuit

### 2024-09-04 jso.tex
knitr

\begin{tcolorbox}[enhanced jigsaw, leftrule=.75mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, colback=white, bottomrule=.15mm, arc=.35mm, breakable, colbacktitle=quarto-callout-note-color!10!white, rightrule=.15mm, bottomtitle=1mm, toptitle=1mm, colframe=quarto-callout-note-color-frame, toprule=.15mm, coltitle=black, opacitybacktitle=0.6, left=2mm, opacityback=0, titlerule=0mm]

>>>>

\begin{tcolorbox}[enhanced jigsaw, title={Algorithm: Jellyfish Optimizer Pseudo Code}, colframe=quarto-callout-note-color-frame, colbacktitle=quarto-callout-note-color!10!white, opacitybacktitle=0.6, arc=.35mm, colback=white, bottomtitle=1mm, opacityback=0, breakable, bottomrule=.15mm, rightrule=.15mm, left=2mm, toprule=.15mm, toptitle=1mm, titlerule=0mm, coltitle=black, leftrule=.75mm]
